---
title: "Figure 1.Reactotype-associated metabolic convergence between oral and gut microbiomes in liver cirrhosis."
author: "Yi Jin"
date: "2026-04-09"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  message = FALSE,
  fig.width = 5,
  fig.height = 5
)
```

## Load packages

```{r}
library(microbiome)
library(DirichletMultinomial)
library(reshape2)
library(magrittr)
library(dplyr)
library(parallel)
library(tidyverse)
library(palmerpenguins)
library(ggdist)
library(ggrepel)
library(ggfun)
library(ggtext)
library(readxl)
library(ggpubr)
library(ggpmisc)
library(knitr)
```

## Data preparation

```{r}
load("dmngut.RData")
load("dmnoral.RData") 

gut.rxty.pcoa.tab <- read.csv("Tables/gut_rxty_pcoa_tab.csv", check.names = FALSE)
oral.rxty.pcoa.tab <- read.csv("Tables/oral_rxty_pcoa_tab.csv", check.names = FALSE)
paired_distances_df.m <- read.csv("Tables/paired_distances_df.csv", check.names = FALSE)

reactotype_colors <- c("#B0E0E6", "#5F9EA0", "#1F78B4") 
severity_color <- c(
  "Healthy" = "gray",
  "Mild Severity" = "cyan",
  "Low Severity" = "skyblue",
  "Moderate Severity" = "blue",
  "High Severity" = "purple"
)

oral.rxty.pcoa.tab$reactotype <- factor(oral.rxty.pcoa.tab$reactotype)
gut.rxty.pcoa.tab$reactotype <- factor(gut.rxty.pcoa.tab$reactotype)

paired_distances_df.m$Severity_group <- factor(
  paired_distances_df.m$Severity_group,
  levels = c("Healthy", "Mild Severity", "Low Severity", "Moderate Severity", "High Severity")
)

H <- read_excel("Tables/Commensal_MSP_FBA_results.xlsx", sheet = "cleaned_Ex")
low <- read_excel("Tables/tMSP_FBA_results.xlsx", sheet = "cleaned_Ex")

colnames(H)[1] <- "Flux"
colnames(low)[1] <- "Flux"

low[] <- lapply(low, function(x) if (is.factor(x)) as.numeric(as.character(x)) else x)
H[] <- lapply(H, function(x) if (is.factor(x)) as.numeric(as.character(x)) else x)
```

------------------------------------------------------------------------

## Fig S1. Reactotype model fitting results.

```{r }
plot(lplc_gutall, type="b", xlab="Number of Dirichlet Components",ylab="Model Fit") 
plot(lplc_oralall, type="b", xlab="Number of Dirichlet Components",ylab="Model Fit") 
```

## Figure 1A. Relative proportions of gut reactotypes.

```{r }
ggplot(gut.rxty.pcoa.tab, aes(x = reactotype, fill = as.factor(Severity_group))) +
  geom_bar(position = "fill") +
  labs(x = "Severity Group", y = "Count", fill = "Reactotype") +
  ggtitle("Relative Proportions Gut Reactotype") +
  scale_fill_manual(values = c("gray", "cyan", "skyblue", "blue", "purple")) +
  theme_minimal()
```

## Figure 1B. Relative proportions of oral reactotypes.

```{r }
ggplot(oral.rxty.pcoa.tab, aes(x = reactotype, fill = as.factor(Severity_group))) +
  geom_bar(position = "fill") +
  labs(x = "Severity Group", y = "Count", fill = "Reactotype") +
  ggtitle("Relative Proportions Oral Reactotype") +
  scale_fill_manual(values = c("gray", "cyan", "skyblue", "blue", "purple")) +  
  theme_minimal()
```

## Figure 1C. MELD between gut reactotypes.

```{r }
ggplot(gut.rxty.pcoa.tab[-which(gut.rxty.pcoa.tab$Severity_group=="Healthy"),], aes(x = reactotype, y = MELD, fill = reactotype)) +
  stat_slab(aes(thickness = stat(pdf*n)),
            scale = 0.7) +
  stat_dotsinterval(side = "bottom", 
                    scale = 0.7, 
                    slab_size = NA)+
  stat_compare_means(comparisons = list(c("1", "2"), c("1", "3"), c("2", "3")), label = "p.format") + 
  labs(x = "Gut Reactotype", y = "MELD") +
  scale_fill_manual(values = reactotype_colors) +
  ggtitle("MELD by Reactotype of LC") +
  theme_minimal()+
  stat_summary(fun.y = mean, geom = "point", shape = 23, size=4)+
  stat_compare_means(aes(group = reactotype), label.y = 53)
```

## Figure 1D. MELD between oral reactotypes.

```{r }
ggplot(oral.rxty.pcoa.tab[-which(oral.rxty.pcoa.tab$Severity_group=="Healthy"),], aes(x = factor(reactotype), y = MELD, fill = factor(reactotype))) +
  stat_slab(aes(thickness = stat(pdf*n)),
            scale = 0.7) +
  stat_dotsinterval(side = "bottom", 
                    scale = 0.7, 
                    slab_size = NA)+
  stat_compare_means(comparisons = list(c("1", "")), label = "p.format") + 
  labs(x = "Oral Reactotype", y = "MELD") +
  scale_fill_manual(values = reactotype_colors[1:2]) +
  ggtitle("MELD by Reactotype of LC") +
  theme_minimal()+
  stat_summary(fun.y = mean, geom = "point", shape = 23, size=4)+
  stat_compare_means(aes(group = reactotype), label.y = 34)
```

## Figure S2C. BMI between gut reactotypes.

```{r }
ggplot(gut.rxty.pcoa.tab[,], aes(x = reactotype, y = BMI, fill = reactotype)) +
  stat_slab(aes(thickness = stat(pdf*n)),
            scale = 0.7) +
  stat_dotsinterval(side = "bottom", 
                    scale = 0.7, 
                    slab_size = NA)+
  labs(x = "Gut Reactotype", y = "BMI") +
  scale_fill_manual(values = reactotype_colors) +
  ggtitle("BMI by Reactotype of LC") +
  theme_minimal()+
  stat_summary(fun.y = mean, geom = "point", shape = 23, size=4)+
  stat_compare_means(aes(group = reactotype))
```

## Figure S2D. Age between gut reactotypes.

```{r }
ggplot(gut.rxty.pcoa.tab[,], aes(x = reactotype, y = Age, fill = reactotype)) +
  stat_slab(aes(thickness = stat(pdf*n)),
            scale = 0.7) +
  stat_compare_means(comparisons = list( c("1", "3")), label = "p.format", hide.ns = TRUE) + #p.signif
  stat_dotsinterval(side = "bottom", 
                    scale = 0.7, 
                    slab_size = NA)+
  labs(x = "Gut Reactotype", y = "Age") +
  scale_fill_manual(values = reactotype_colors) +
  ggtitle("Age by Reactotype of LC") +
  theme_minimal()+
  stat_summary(fun.y = mean, geom = "point", shape = 23, size=4)+
  stat_compare_means(aes(group = reactotype), label.y = 90)

```

## Figure S2E. BMI between oral reactotypes.

```{r }
ggplot(oral.rxty.pcoa.tab[-which(oral.rxty.pcoa.tab$Severity_group=="Healthy"),], aes(x = factor(reactotype), y = BMI, fill = factor(reactotype))) +
  stat_slab(aes(thickness = stat(pdf*n)),
            scale = 0.7) +
  stat_dotsinterval(side = "bottom", 
                    scale = 0.7, 
                    slab_size = NA)+
  # stat_compare_means(comparisons = list(c("1", "2")), label = "p.signif") +
  labs(x = "Oral Reactotype", y = "BMI") +
  scale_fill_manual(values = reactotype_colors[1:2]) +
  ggtitle("BMI by Reactotype of LC") +
  theme_minimal()+
  stat_summary(fun.y = mean, geom = "point", shape = 23, size=4)+
  stat_compare_means(aes(group = reactotype), label.y = 55)
```

## Figure S2F. Age between oral reactotypes.

```{r }
ggplot(oral.rxty.pcoa.tab[-which(oral.rxty.pcoa.tab$Severity_group=="Healthy"),], aes(x = factor(reactotype), y = Age, fill = factor(reactotype))) +
  stat_slab(aes(thickness = stat(pdf*n)),
            scale = 0.7) +
  stat_dotsinterval(side = "bottom", 
                    scale = 0.7, 
                    slab_size = NA)+
  # stat_compare_means(comparisons = list(c("1", "2")), label = "p.signif") +
  labs(x = "Oral Reactotype", y = "Age") +
  scale_fill_manual(values = reactotype_colors[1:2]) +
  ggtitle("Age by Reactotype of LC") +
  theme_minimal()+
  stat_summary(fun.y = mean, geom = "point", shape = 23, size=4)+
  stat_compare_means(aes(group = reactotype), label.y = 76)
```

## Figure 1E. Oral-gut metabolic distance (OGMD) by severity groups.

```{r }
ggplot(paired_distances_df.m, aes(x = Severity_group, y = Paired_Distance, fill = Severity_group)) +
  stat_slab(aes(thickness = stat(pdf*n)),
            scale = 0.7) +
  stat_dotsinterval(side = "bottom", 
                    scale = 0.7, 
                    slab_size = NA)+
  labs(x = "Severity", y = "Oral-gut Rxbiome Bray distance", fill = "Severity group")+
  ggtitle("Boxplot of oral-gut distance by severity")+
  scale_fill_manual(values = severity_color, labels = c("Healthy","Mild Severity (3-8)", "Low Severity (9-14)", "Moderate Severity (15-24)", "High Severity (≥25)")) +
  theme_minimal()+
  stat_summary(fun.y = mean, geom = "point", shape = 23, size=4)+
  stat_compare_means(aes(group = Severity_group), label.y = 0.95)+
  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
  stat_compare_means(comparisons = list(
    # c("Healthy","Mild Severity"),
    # c("Healthy", "Low Severity"),
    # c("Healthy", "Moderate Severity"),
    c("Moderate Severity", "High Severity"),
    c("Healthy", "High Severity")
  ), label = "p.format") 
```

## Figure 1F. OGMD and MELD (cirrhosis severity) associations.

```{r }
ggplot(paired_distances_df.m[-which(is.na(paired_distances_df.m$MELD)),], 
             aes(x = MELD, y = Paired_Distance)) +  
  geom_point(aes(color = distance_group), size = 4) +  
  geom_smooth(method = "lm", se = TRUE, color = "black") +  
  labs(x = "MELD", y = "Oral-gut Reactobiome Distance") +  
  # ggtitle("Linear Regression between MELD and OGD") +  # Add title
  scale_color_manual(values = c("high_distance" = "#809FFF", "low_distance" = "#00008B")) +  # Specify colors
  stat_poly_eq(aes(label = paste(..rr.label.., ..p.value.label.., sep = "~~~")), 
               label.x = 0.1, label.y = 0.1,  # Adjust these values for the p-value label position based on data coordinates
               formula = y ~ x, parse = TRUE, size = 6) +  # Increase font size for the equation label
  theme(
    plot.title = element_text(size = 15),  # Increase title font size
    axis.title.x = element_text(size = 15),  # Increase x-axis label font size
    axis.title.y = element_text(size = 15),  # Increase y-axis label font size
    axis.text = element_text(size = 15),  # Increase axis text size
    legend.text = element_text(size = 13),  # Increase legend text size
    # legend.title = element_text(size = 13),  # Increase legend title font size
    legend.title = element_blank(),  # Remove legend title
    legend.position = "top",  # Move legend to the top
    # legend.position = c(0.4, 0.2),  # Set legend position inside the plot (x = 0.8, y = 0.8)
    legend.direction = "horizontal",  # Arrange legend horizontally
    panel.background = element_rect(fill = "white", color = NA),  # Set panel background to white
    plot.background = element_rect(fill = "white", color = NA),  # Set overall plot background to white
    panel.grid.major = element_blank(),  # Remove major grid lines
    panel.grid.minor = element_blank()   # Remove minor grid lines
  )

```

## Figure 1I. Wilcoxon test for predicted metabolic producion.

## Statistical results & Volcano plot

```{r }
merged_data <- merge(low, H, by = "Flux", all = TRUE)
merged_data[is.na(merged_data)] <- 0
wilcoxon_test_results <- apply(merged_data[, -1], 1, function(row) {
  low_values <- as.numeric(row[1:(ncol(low) - 1)])
  H_values <- as.numeric(row[(ncol(low)):(ncol(merged_data) - 1)])
  
  wilcoxon_test <- wilcox.test(low_values, H_values)
  
  low_mean <- mean(low_values)
  H_mean <- mean(H_values)
  
  log2fc_low_H <- log2((low_mean + 0.000001) / (H_mean + 0.000001))
  
  return(c(low_mean, H_mean, log2fc_low_H, wilcoxon_test$p.value))
})

# data frame
wilcoxon_test_results_df <- data.frame(
  Metabolite = merged_data$Flux,
  Low_Mean = wilcoxon_test_results[1, ],
  H_Mean = wilcoxon_test_results[2, ],
  log2FC_Low_H = wilcoxon_test_results[3, ],
  p_value = wilcoxon_test_results[4, ]
)

# show stats results
print(wilcoxon_test_results_df)


library(readxl)
FBA_16MSP_stat_for_volcano <- read_excel("Tables/FBA_16MSP_stat_for_volcano.xlsx")

data = FBA_16MSP_stat_for_volcano
data$log10_p = -log(data$p_value,10)

# volcano
ggplot(data = data) +
  geom_point(aes(x = log2FoldChange, y = -log10(p_value),
                 color = log2FoldChange,
                 size = -log10(p_value))) +
  geom_point(data = data %>%
               tidyr::drop_na() %>%
               dplyr::filter(change != "Normal") %>%
               dplyr::arrange(desc(-log10(p_value))) %>%
               dplyr::slice(1:20),
             aes(x = log2FoldChange, y = -log10(p_value),
                 size = -log10(p_value)),
             shape = 21, show.legend = FALSE, color = "#000000") +
  geom_text_repel(data = data %>%
                    tidyr::drop_na() %>%
                    dplyr::filter(change != "Normal") %>%
                    dplyr::arrange(desc(-log10(p_value))) %>%
                    dplyr::slice(1:15) %>%
                    dplyr::filter(change == "Up"),
                  aes(x = log2FoldChange, y = -log10(p_value), label = SYMBOL),
                  box.padding = 0.5,
                  nudge_x = 0.5,
                  nudge_y = 0.2,
                  segment.curvature = -0.1,
                  segment.ncp = 3,
                  direction = "y",
                  hjust = "left") +
  scale_color_gradientn(
    colours = c("#3288bd", "#66c2a5", "#ffffbf", "#f46d43", "#9e0142"),
    values = scales::rescale(c(-20, -10, 0, 10, 20), to = c(0, 1))
  ) +
  geom_vline(xintercept = c(-log2(1.5), log2(1.5)), linetype = 2) +
  geom_hline(yintercept = -log10(0.05), linetype = 4) +
  xlim(c(-20,20)) +
  ylim(c(-1, 10)) +
  theme_bw() +
  theme(panel.grid = element_blank(),
        legend.background = element_roundrect(color = "#808080", linetype = 1),
        axis.text = element_text(size = 13, color = "#000000"),
        axis.title = element_text(size = 15),
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  annotate(geom = "text", x = 15, y = 2, label = "p = 0.05", size = 5) +
  coord_cartesian(clip = "off") +
  annotation_custom(
    grob = grid::segmentsGrob(
      y0 = unit(-10, "pt"),
      y1 = unit(-10, "pt"),
      arrow = arrow(angle = 45, length = unit(.2, "cm"), ends = "first"),
      gp = grid::gpar(lwd = 3, col = "#74add1")
    ),
    xmin = -20,
    xmax = -1,
    ymin = 10,
    ymax = 10
  ) +
  annotation_custom(
    grob = grid::textGrob(
      label = "Down",
      gp = grid::gpar(col = "#74add1")
    ),
    xmin = -20,
    xmax = -1,
    ymin = 10,
    ymax = 10
  ) +
  annotation_custom(
    grob = grid::segmentsGrob(
      y0 = unit(-10, "pt"),
      y1 = unit(-10, "pt"),
      arrow = arrow(angle = 45, length = unit(.2, "cm"), ends = "last"),
      gp = grid::gpar(lwd = 3, col = "#d73027")
    ),
    xmin = 20,
    xmax = 1,
    ymin = 10,
    ymax = 10
  ) +
  annotation_custom(
    grob = grid::textGrob(
      label = "Up",
      gp = grid::gpar(col = "#d73027")
    ),
    xmin = 20,
    xmax = 1,
    ymin = 10,
    ymax = 10
  )
```

## Figure 1J. FBA & FVA predicted NH3 flux.

```{r }
FBA_FVA_long <- read.csv("Tables/FBA_FVA_long.csv", check.names = FALSE)
FBA_FVA_long_H <- read.csv("Tables/FBA_FVA_long_H.csv", check.names = FALSE)

ggplot(FBA_FVA_long, aes(x = species, y = variable, fill = value)) + 
  geom_tile(width = 0.9, height = 0.9) + 
  labs(x = element_blank(), y = element_blank(), fill = "Flux Value") + 
  theme_classic() + 
  theme(legend.position = "bottom", 
        axis.text.x = element_text(angle = 0, hjust = 1)) + 
  geom_text(data = subset(FBA_FVA_long, value == 0), aes(label = "X")) + 
  scale_fill_gradient(low = "white", high = "blue", na.value = "white", limits = c(0, 5))+
  coord_flip()


ggplot(FBA_FVA_long_H, aes(x = species, y = variable, fill = value)) + 
  geom_tile(width = 0.9, height = 0.9) + 
  labs(x = element_blank(), y = element_blank(), fill = "Flux Value") + 
  theme_classic() + 
  theme(legend.position = "bottom", 
        axis.text.x = element_text(angle = 90, hjust = 1)) + 
  geom_text(data = subset(FBA_FVA_long_H, value == 0), aes(label = "X")) + 
  scale_fill_gradient(low = "white", high = "blue", na.value = "white")
```

## Figure 1K. Predicted NH3 production accross different diets.

```{r }
Predicted_NH3_tMSPs <- read.csv("Tables/Predicted_NH3_tMSPs.csv", check.names = FALSE)

set2_colors <- RColorBrewer::brewer.pal(6, "Set2")

custom_colors <- c(
  UK_avg_FBA = set2_colors[1],
  UK_avg_FVA = set2_colors[6],
  HFD_P      = set2_colors[2],
  HFD_O      = set2_colors[3],
  HPD_P      = set2_colors[4],
  HPD_O      = set2_colors[5]
)

ggplot(Predicted_NH3_tMSPs, aes(x = reorder(species, Flux), y = Flux)) +
  geom_boxplot(
    fill = "grey",
    color = "black",
    width = 0.5,
    outlier.shape = 21,
    outlier.alpha = 0.5,
    linewidth = 0.4
  ) +
  geom_jitter(
    aes(color = Condition),
    size = 2,
    width = 0.15,
    alpha = 0.8
  ) +
  coord_flip() +
  theme_bw(base_size = 12) +
  labs(
    x = "Species",
    y = "Estimated ammonia production"
  ) +
  scale_color_manual(
    values = custom_colors,
    name = "Diet"
  ) +
  theme(
    panel.grid.major.x = element_blank(),
    panel.grid.minor = element_blank(),
    axis.text.y = element_markdown(face = "italic"),
    axis.text = element_text(color = "black"),
    legend.title = element_text(size = 11, face = "bold"),
    legend.text = element_text(size = 10),
    panel.border = element_rect(color = "black", size = 0.4)
  )
```

## Figure 1L. Predicted acetate production across different diets.

```{r }
Predicted_acetate_tMSPs <- read.csv("Tables/Predicted_acetate_tMSPs.csv", check.names = FALSE)

ggplot(Predicted_acetate_tMSPs, aes(x = reorder(species, Flux), y = Flux)) +
  geom_boxplot(
    fill = "grey",
    color = "black",
    width = 0.5,
    outlier.shape = 21,
    outlier.alpha = 0.5,
    linewidth = 0.4
  ) +
  geom_jitter(
    aes(color = Condition),
    size = 2,
    width = 0.15,
    alpha = 0.8
  ) +
  coord_flip() +
  theme_bw(base_size = 12) +
  labs(
    x = "Species",
    y = "Estimated acetate production"
  ) +
  scale_color_manual(
    values = custom_colors,
    name = "Diet"
  ) +
  theme(
    panel.grid.major.x = element_blank(),
    panel.grid.minor = element_blank(),
    axis.text.y = element_markdown(face = "italic"),
    axis.text = element_text(color = "black"),
    legend.title = element_text(size = 11, face = "bold"),
    legend.text = element_text(size = 10),
    panel.border = element_rect(color = "black", size = 0.4)
  )

```

## Figure 1M. Correlation analysis of relative abundance with disease severity.

```{r }
# stat
gut_16MSP_MELD <- read.csv("Tables/gut_16MSP_MELD.csv", check.names = FALSE)

MSP_16 = c("msp_0005", "msp_0166", "msp_0313", "msp_0380", "msp_0570","msp_0573", 
           "msp_0627", "msp_0881", "msp_0884","msp_1219", "msp_1782", "msp_1786", 
           "msp_1787","msp_1788", "msp_1793", "msp_1799")
cor_gut16_MELD_results <- data.frame(msp = MSP_16, correlation = NA, p_value = NA)

for (i in seq_along(MSP_16)) {
  msp_col <- MSP_16[i]
  
  test_result <- cor.test(gut_16MSP_MELD[[msp_col]], gut_16MSP_MELD$MELD, method = "spearman")
  
  cor_gut16_MELD_results$correlation[i] <- test_result$estimate
  cor_gut16_MELD_results$p_value[i] <- test_result$p.value
}

cor_gut16_MELD_results$FDR <- p.adjust(
  cor_gut16_MELD_results$p_value,
  method = "BH"
)

# View stats results
print(cor_gut16_MELD_results)

# Corr plot
cor_gut16_MELD_results$significance <- ifelse(cor_gut16_MELD_results$FDR <= 0.001, "***",
                                              ifelse(cor_gut16_MELD_results$FDR <= 0.01, "**",
                                                     ifelse(cor_gut16_MELD_results$FDR <= 0.05, "*",
                                                            ifelse(cor_gut16_MELD_results$FDR <= 0.1, "·", ""))))
cor_gut16_MELD_results$msp <- factor(
  cor_gut16_MELD_results$msp,
  levels = cor_gut16_MELD_results$msp[order(cor_gut16_MELD_results$correlation)]
)

ggplot(cor_gut16_MELD_results, aes(x = "MELD", y = msp)) +
  geom_tile(aes(fill = correlation), color = "white") +
  scale_fill_gradient2(
    low = "dodgerblue",
    mid = "white",
    high = "firebrick",
    midpoint = 0,
    limits = c(-0.4, 0.4),
    name = "Spearman\nrho"
  ) +
  geom_text(aes(label = significance), color = "black", size = 5) +
  labs(
    x = "",
    y = "Gut MSPs"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 0, hjust = 0.5),
    axis.text.y = element_text(size = 8),
    panel.grid = element_blank()
  )

```

## Figure 1N. Co-abundance analysis of 16 tMSPs.

Code for making the table suitable for Cytoscape visualization.

```{r }
abundance_data_t <- read.csv("Tables/abundance_data_t.csv", row.names = 1)
abundance_data_t <- as.data.frame(abundance_data_t)
abundance_data_t[] <- lapply(abundance_data_t, function(x) as.numeric(as.character(x)))
feature_names <- colnames(abundance_data_t)

## Spearman stat

edge_list <- data.frame(
  source = character(),
  target = character(),
  correlation = numeric(),
  p_value = numeric(),
  stringsAsFactors = FALSE
)

for (i in 1:(ncol(abundance_data_t) - 1)) {
  for (j in (i + 1):ncol(abundance_data_t)) {
    
    feature1 <- colnames(abundance_data_t)[i]
    feature2 <- colnames(abundance_data_t)[j]
    
    x <- abundance_data_t[[i]]
    y <- abundance_data_t[[j]]
    
    complete_idx <- complete.cases(x, y)
    x_use <- x[complete_idx]
    y_use <- y[complete_idx]
    
    if (length(x_use) < 3) next
    
    if (sd(x_use) == 0 || sd(y_use) == 0) next
    
    cor_test_spearman <- suppressWarnings(
      cor.test(x_use, y_use, method = "spearman", exact = FALSE)
    )
    
    edge_list <- rbind(
      edge_list,
      data.frame(
        source = feature1,
        target = feature2,
        correlation = unname(cor_test_spearman$estimate),
        p_value = cor_test_spearman$p.value,
        stringsAsFactors = FALSE
      )
    )
  }
}

# FDR
edge_list$FDR <- p.adjust(edge_list$p_value, method = "BH")

# Table for Cytoscape network visualization
edge_list <- edge_list %>%
  mutate(
    abs_correlation = abs(correlation),
    correlation_sign = ifelse(correlation > 0, "positive", "negative"),
    significance = case_when(
      FDR <= 0.001 ~ "***",
      FDR <= 0.01  ~ "**",
      FDR <= 0.05  ~ "*",
      FDR <= 0.1   ~ "·",
      TRUE ~ ""
    )
  )

cytoscape_edges_all <- edge_list %>%
  arrange(FDR, desc(abs_correlation))

cytoscape_edges_filtered <- cytoscape_edges_all %>%
  filter(FDR <= 0.05)

head(cytoscape_edges_filtered)
```
